Title

### 2023-11-17 main.tex
Derp

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
% \cpnote{Revisar}
Pauli channels are fundamental in the context of quantum computing as they
model the simplest kind of noise in quantum devices.  We propose a quantum
algorithm for simulating
Pauli channels 
and extend it to encompass Pauli dynamical maps 
(parametrized Pauli channels).
A parametrized quantum circuit is employed to accommodate for dynamical maps. 
We also establish the mathematical conditions for an
$N$-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is reported. 
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}

@@

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a general and straightforward quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for several single and two-qubit Pauli channels.
Expanding beyond Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps\cpnote{Me parece que las dos frases anteriores 
dicen casi lo mismo. Poner una sola frase}.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem, which  sets
the mathematical conditions for the transformations that can be done using a
parametrized circuit with the restriction that only a controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in section
\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. 
% \revnote{So another way to see this is that the simulation through the
% proposed decomposition works only for depolarising channels, and fails
% otherwise. } 
% \tbnote{Contestar en la carta que funciona hasta cierto punto para todos los
% canales propuestos y que se cuantifica qué tan bien funciona o no usando la
% fidelidad}
This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
% Moreover, the algorithm of \fref{Fig2} is not optimal for
% unitary channels (that is, the channels corresponding to the vertices of the
% tetrahedron). \revnote{why?} \tbnote{Replantear, decir que cerca de los vertices del tetraedro teneos una fidelidad
% baja segun la imagen, por lo que podemos ver que los unitarios
% tienen una fid baja.} 
% \tbnote{
Moreover, as can be seen in \fref{Fig3}, the algorithm of \fref{Fig2} is not optimal for 
channels in the edges of the tetrahedron, which corresponds to unitary channels. 
% }
These channels could be accomplished more
efficiently by simply applying the corresponding unitary operator directly. 
% \revnote{I wholeheartedly agree with this statement, and I would go so far as
% to claim that this is true in general, even at the center of the tethraedron.}
% \tbnote{Este comentario se conecta con lo del 
% primer comentario, que no sé bien cómo contestar.}
% Nevertheless, due to its general design to accommodate any Pauli channel, the
% algorithm employs numerous quantum gates even in such scenarios. 
In this case we would be trading generality for fidelity. 
% \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
% \tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
The main advantage of the algorithm is that we can simulate with a unitary 
circuit
% simple, and if we want 
% to 
any Pauli channel, 
% (for example,
% for simulating a Pauli dynamical map as we will see later),
only varying a couple of angles in the circuit.
%  to move between 
% different Pauli channels and not completely reconstruct the circuit. 
In fact, as we will see, sometimes only changing one angle in the circuit will
be enough to simulate many non-unitary dynamical maps of physical interest. 
\cpnote{Revisa estas ultimas frases. Reformule lo que pusiste.}

% {\color{green} This disadvantage comes from the fact
% that the circuit is applicable to any Pauli channel, which that means that sometimes
% it is not the most straightforward algorithm to simulate a Pauli channel.
% However, the main advantages are that the algorithm is simple, and if we want 
% to simulate many Pauli channels (for example,
% for simulating a Pauli dynamical map as we will see later),
% we only have to change a couple of angles in the circuit to move between 
% different Pauli channels and not completely reconstruct the circuit. 
% And as we will see, sometimes only changing
% one angle in the circuit will be enough.}\\
% $\;$\\
% 
% \tbnote{Sección que agregué:}\\
% }}}
\subsection{Simulation of a two-qubit Pauli channel} \label{2qbit} % {{{
% {\color{green}
For the general case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} requires two main
qubits and four ancilla qubits.
% , on which it would be necessary to create the state $\sum_{\vec{\gamma}}
% b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, the quantum computer which we are using has only \cpnote{cuantos qubits 
tiene esa compu?}.
does not have that many qubits,
We can still simulate a two qubit Pauli channel that does not apply all 
two-qubit Pauli matrices to the system\cpnote{that applies at most tantos operaciones 
de Pauli}.
For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has four Pauli operations, 
only $2$ ancilla qubits will be necessary, and thus it can be implemented
using the circuit of \fref{2qbit}b.

\begin{figure} % {{{
\centering
\includegraphics{images/qbit-im.pdf}
\caption{{\bf Circuit for 2-qubit dephasing channel.}  Circuit implementation
for the 2-qubit dephasing channel of \eref{2qbit-c}. The state on the two
ancilla qubits can be constructed just as it was done for \fref{Fig2}.
\cpnote{Este caption no está copleto. Falta describir la a y luego la b. De hecho 
dado que primero proponemos el circuito y luego vemos la fidelidad, propngo 
poenr el circuito arriba y la fidelidad abajo. TAbien describir ambas cosas. } }
\label{2qbit}
\end{figure} % }}}

Just as for the one-qubit Pauli channels, this 
channel was implemented on IBM's ibmq-lima  quantum computer. We obtained the Choi 
matrix by doing quantum process tomography on
the main qubits. Then, we calculated the diamond fidelity for different values of $p$ and
obtained the results shown in \fref{2qbit}a. 
As can be seen in the figure, the fidelity doesn't vary much as we change the value of $p$.
It stays at a value of around $0.75$, and it is biggest around $p=0$,
corresponding to the identity channel\cpnote{Una descripcion mas precisa de
estos valores por favor.}
% }

@@

\tbnote{Buscar alguna forma fácil de probar que no todos los mapas tienen la forma de 1PR} 
\end{itemize}

@@

Then, when working with Pauli dynamical maps,
we searched for a way of minimizing the amount of 
parametric operations in the circuit 
by requiring that only one single-qubit rotation depends on the parameter. 
% \revnote{This reasoning I miss, simplifying for achieving what goal? } 
% \tbnote{Le di una reescritura a esa frase.}
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.
\tbnote{Given this condition, we considered the space of Pauli maps that are
possible to parametrize with one parameter, and gave some explicit examples for
a system of one qubit.  As the number of qubits gets bigger, the degrees of
freedom for choosing a Pauli dynamical map also gets bigger, so we would expect
that the space of maps that can be done with only one parameter
becomes a relatively smaller part of the whole space of Pauli dynamical maps.
However, some paradigmatic maps as the dephasing one we studied for 2 qubits in
section \ref{2qbit} will still be possible to do with a 1PR circuit (for this
case, this can be seen by noticing that said dephasing channel in
\eref{2qbit-c} has the same form as the depolarizing channel of \eref{eq:depo},
which we proved to be possible to implement with a 1PR circuit).}
\cpnote{Reescribe lo anterior sin hacer referencias a ecuaciones o secciones.}

>>>>

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Pauli channels are fundamental in the context of quantum computing as they
model the simplest kind of noise in quantum devices.  We propose a quantum
algorithm for simulating
Pauli channels 
and extend it to encompass Pauli dynamical maps 
(parametrized Pauli channels).
A parametrized quantum circuit is employed to accommodate for dynamical maps. 
We also establish the mathematical conditions for an
$N$-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is reported. 
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}

@@

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a general and straightforward quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for several single and two-qubit Pauli channels.
Expanding beyond Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels. In fact, in order  to implement them, we study parametrized quantum
circuits in chapter \ref{sec: 1PR Circuits}. Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem, which  sets
the mathematical conditions for the transformations that can be done using a
parametrized circuit with the restriction that only a controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in section
\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. 
% \revnote{So another way to see this is that the simulation through the
% proposed decomposition works only for depolarising channels, and fails
% otherwise. } 
% \tbnote{Contestar en la carta que funciona hasta cierto punto para todos los
% canales propuestos y que se cuantifica qué tan bien funciona o no usando la
% fidelidad}
This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
% Moreover, the algorithm of \fref{Fig2} is not optimal for
% unitary channels (that is, the channels corresponding to the vertices of the
% tetrahedron). \revnote{why?} \tbnote{Replantear, decir que cerca de los vertices del tetraedro teneos una fidelidad
% baja segun la imagen, por lo que podemos ver que los unitarios
% tienen una fid baja.} 
% \tbnote{
Moreover, as can be seen in \fref{Fig3}, the algorithm of \fref{Fig2} is not optimal for 
channels in the edges of the tetrahedron, which corresponds to unitary channels. 
% }
These channels could be accomplished more
efficiently by simply applying the corresponding unitary operator directly. 
% \revnote{I wholeheartedly agree with this statement, and I would go so far as
% to claim that this is true in general, even at the center of the tethraedron.}
% \tbnote{Este comentario se conecta con lo del 
% primer comentario, que no sé bien cómo contestar.}
% Nevertheless, due to its general design to accommodate any Pauli channel, the
% algorithm employs numerous quantum gates even in such scenarios. 
In this case we would be trading generality for fidelity. 
% \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
% \tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
The main advantage of the algorithm is that we can simulate with a unitary 
circuit
% simple, and if we want 
% to 
any Pauli channel, 
% (for example,
% for simulating a Pauli dynamical map as we will see later),
only varying a couple of angles in the circuit.
%  to move between 
% different Pauli channels and not completely reconstruct the circuit. 
In fact, as we will see, sometimes only changing one angle in the circuit will
be enough to simulate many non-unitary dynamical maps of physical interest.

% {\color{green} This disadvantage comes from the fact
% that the circuit is applicable to any Pauli channel, which that means that sometimes
% it is not the most straightforward algorithm to simulate a Pauli channel.
% However, the main advantages are that the algorithm is simple, and if we want 
% to simulate many Pauli channels (for example,
% for simulating a Pauli dynamical map as we will see later),
% we only have to change a couple of angles in the circuit to move between 
% different Pauli channels and not completely reconstruct the circuit. 
% And as we will see, sometimes only changing
% one angle in the circuit will be enough.}\\
% $\;$\\
% 
% \tbnote{Sección que agregué:}\\
% }}}
\subsection{Simulation of a two-qubit Pauli channel} \label{2qbit-s} % {{{
% {\color{green}
For the general case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} requires two main
qubits and four ancilla qubits.
% , on which it would be necessary to create the state $\sum_{\vec{\gamma}}
% b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, the quantum computer which we are using has only 5 qubits.
We could still simulate a two qubit Pauli channel that applies at most $8$ Pauli operations,
instead of 16 which would be the most general case,
using the three ancilla qubits. 
For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has four Pauli operations, 
only $2$ ancilla qubits will be necessary, and thus it can be implemented
using the circuit of \fref{2qbit}b.

\begin{figure} % {{{
\centering
\includegraphics{images/qbit-im.pdf}
\caption{{\bf Circuit for 2-qubit dephasing channel.}  Circuit implementation
for the 2-qubit dephasing channel of \eref{2qbit-c} and fidelity results of its implementation using ibmq-lima.
 The circuit is shown in figure a), where the  state on the two
ancilla qubits can be constructed just as it was done for \fref{Fig2}. 
In figure b) we show the results of fidelities after implementing
this circuit on ibmq-lima for $25$ values of $p$ between $0$ and $1$, 
each of which is simulated $10$ times.
}
\label{2qbit}
\end{figure} % }}}

Just as for the one-qubit Pauli channels, this 
channel was implemented on IBM's ibmq-lima  quantum computer. We obtained the Choi 
matrix by doing quantum process tomography on
the main qubits. Then, we calculated the diamond fidelity for different values of $p$ and
obtained the results shown in \fref{2qbit}a. 
As can be seen in the figure, the fidelity doesn't vary much as we change the value of $p$.
The average fidelity over all values of $p$ is $0.758$ and it is biggest when $p=0$,
corresponding to the identity channel, where it reaches a fidelity of $0.874$.

@@

\end{itemize}

@@

Then, when working with Pauli dynamical maps,
we searched for a way of minimizing the amount of 
parametric operations in the circuit 
by requiring that only one single-qubit rotation depends on the parameter. 
% \revnote{This reasoning I miss, simplifying for achieving what goal? } 
% \tbnote{Le di una reescritura a esa frase.}
In theorem \ref{theorem2} we found the general mathematical conditions for 
this, applicable to any parametrized circuit.
Given this condition, we considered the space of Pauli maps that are
possible to parametrize with one parameter, and gave some explicit examples for
a system of one qubit.  As the number of qubits gets bigger, the degrees of
freedom for choosing a Pauli dynamical map also gets bigger, so we would expect
that the space of maps that can be done with only one parameter
becomes a relatively smaller part of the whole space of Pauli dynamical maps.
However, some paradigmatic maps as the dephasing one we studied for 2 qubits will still be possible to do with a 1PR circuit (for this
case, this can be seen by noticing that said dephasing channel
has the same form as the depolarizing channel for one qubit,
which we proved to be possible to implement with a 1PR circuit).
